---
title: "Alcohol vs Seat choice"
author: "Bella Verdin"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

#Introduction
 
The research question is this: Is there a difference in the amount of alcohol consumed per week by students who sit in row 1, row 2, or row 3 of the UC Davis classroom.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 

#Methods

We are trying to predict alcohol consumption based o seating row. 

Data Form UC Davis:

alcohol ~ Seat

alcohol is a numerical variable

seat is a categorical variable

So we use the numerical~cat helper file.

#Description

##Graphical Description

```{r}
boxplot(alcohol~Seat,data=davisdata)
```


This box plot shows me that there is a significant difference within the back rows when it comes to consumption vs the middle. Based on the plot, the students in the back row seem to take in more alcohol. 

##Numerical Description

```{r}
favstats(alcohol~Seat,data=davisdata)
```

From what the table shows me the back row has a mean of 9.6, the front row having a mean of 1.8 and the middle row with 3.2. showing that the students in the back rows drink more frequently. 


## Inferential Description

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


The p-value shows to be 0.000116. which means that students in every row do not consume the same amount of alcohol. 

```{r}
plot(TukeyHSD(model1))
```

Using the Tukey HSD test I found that people seated in the back rows drink more vs the people in the middle and front. there seems to be no difference in the alcohol consumption between the middle ad front rows. 


## Conclusions

I am trying to see if there happens to be a difference in students who in take alcohol in rows 1,2, and 3. With the p-value of 0.000116 which is less than 0.05 makes me reject the null hypothesis, once the graph are read it is known that the students in the back row drink more. 
